Adding selection to \stdpopsim: oh how the tables have turned

### 2025-01-10 analysis2_manuscript.tex
Update analysis2_manuscript.tex

    Using \stdpopsim, we can easily simulate genetic data under a model of selection and then 
    examine the performance of different methods for inferring $N_e(t)$ from these simulated 
    data. In Figure \ref{fig:1pop-human-demography}, we show the results of such a benchmark
    where we have simulated genomes under a model of human out of Africa (OOA) demography
    with and without purifying selection acting on exons.
    For this simulation we have used
    a genetic map from the HapMap Project \citep{international2007second} along with a
    DFE for deleterious alleles (estimated by \cite{huber2017determining})
    that acts on exonic \kelcomment{do you mean exonic, or nonsynonymous?} positions defined from the HAVANA group release 104 for the human genome.
    % DRS: Maybe we should say something about how easy it was to do these simulations, and maybe even show
    % some example code somewhere to prove our point? Could help emphasize the utility of this resource.
    These simulations were then used to estimate $N_e(t)$ using four methods: 1) \msmc \citep{Schiffels2020}, 
    2) \stairway \citep{liu2020stairway}, 3) \gone \citep{santiago2020recent}, and 4) \smcpp \citep{terhorst2017robust}.
    In this and what follows we performed 3 replicate whole genome simulations, so uncertainty in estimates might
    be roughly assessed.
    However, as a thorough benchmarking is not the main purpose of this manuscript, we saved computational resources by not conducting more simualtion replicates.

>>>>

    Using \stdpopsim, we can easily simulate genetic data under a model of selection and then 
    examine the performance of different methods for inferring $N_e(t)$ from these simulated 
    data. In Figure \ref{fig:1pop-human-demography}, we show the results of such a benchmark
    where we have simulated genomes under a model of human out of Africa (OOA) demography
    with and without purifying selection acting on exons.
    For this simulation we have used
    a genetic map from the HapMap Project \citep{international2007second} along with a
    DFE for deleterious alleles (estimated by \cite{huber2017determining})
    that acts on exonic \kelcomment{do you mean exonic, or nonsynonymous?} positions defined from the HAVANA group release 104 for the human genome.
    % DRS: Maybe we should say something about how easy it was to do these simulations, and maybe even show
    % some example code somewhere to prove our point? Could help emphasize the utility of this resource.
    These simulations were then used to estimate $N_e(t)$ using four methods: 1) \msmc \citep{Schiffels2020}, 
    2) \stairway \citep{liu2020stairway}, 3) \gone \citep{santiago2020recent}, and 4) \smcpp \citep{terhorst2017robust}.
    In this and what follows we performed 3 replicate whole genome simulations, so uncertainty in estimates might
    be roughly assessed.
    However, as a thorough benchmarking is not the main purpose of this manuscript, we saved computational resources by not conducting more simulation replicates.
